Parallelization of Fast $\ell_1$-Minimization for Face Recognition

### 2011-05-23 main.tex
Working on cache figures
Added abstract

\usepackage{cvpr}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}

@@

\begin{abstract}

\end{abstract}

@@

\begin{figure}
\begin{center}
\includegraphics[width=3.5in]{figures/caches}
\end{center}
\caption{Scale Drawing of the CPU and GPU cache sizes}
\label{fig:caches}
\end{figure}

>>>>

\usepackage{cvpr}
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
\usepackage{times}
\usepackage{epsfig}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{subfigure}

@@

\begin{abstract} Recently a family of promising face recognition algorithms
that are based on sparse representation and $\ell_1$ minimization have been
been developed.  These algorithms have not yet seen commercial application,
largely due to their greater computational requirements compared to more
traditional algorithms.  This paper studies techniques for leveraging the
massive parallelism available in GPU and multi-core CPU hardware to accelerate
augmented Lagrangian method (ALM) based $\ell_1$ minimization solvers.  The
proposed implementations are significantly faster than than previously
published implementations.  Despite the low arithmetic intensity of ALM
solvers, the GPU can still outperform the CPU by a wide margin for large
problem sizes, and when solving many small problems simultaneously.  The
proposed CPU implementation remains faster for solving a single moderately
sized problem.  \end{abstract}

@@

\begin{figure}
\centering
\subfigure[The larger algorithm data structures]
{
	\includegraphics[scale=1.2]{figures/arrays}
	\label{fig:arrays}
}
\subfigure[The caches on a E5530 CPU]
{
	\includegraphics[scale=1.2]{figures/cpu_caches}
	\label{fig:cpu_caches}
}
\subfigure[The caches on a GTX480 GPU]
{
	\includegraphics[scale=1.2]{figures/gpu_caches}
	\label{fig:gpu_caches}
}
\caption{Scale drawings for the visual comparison of the algorithm
working set to available caches}
\end{figure}
